### 2025-03-21 README.Rmd
add runs and rmd inspections and clean up
commit namespace things

5. For EBS Pcod, age data has only been used when there exists alredy pre-processed length data associated with it. I.e., I matched the y2 length data object recieved from Steve with age data I downloaded when testing the baseISS functionality on age data. This was necessary becasue I needed quantities like YAGM_SNUM to perform the weighted expansion.

@@

- subsampling

>>>>

5. For EBS Pcod, age data has only been used when there exists already pre-processed length data associated with it. I.e., I matched the y2 length data object recieved from Steve with age data I downloaded when testing the baseISS functionality on age data. This was necessary becasue I needed quantities like YAGM_SNUM to perform the weighted expansion.

@@

- subsampling length - done.

- custom max length control - done.
- plus group option - done.
- different length bin size control - done.
- different species - tested with Pollock only.
- reboot_age.R
